Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-12-05 manuscript/manuscript.Rmd
anesthesiology submission

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
author:
- name: Aaron Conway
  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
  url: https://www.aaronconway.info
- name: Megan Bittner
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Dan Phan
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Navpreet Kamboj
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
- name: Kristina Chang
  affiliation: Toronto General Hospital, UHN
- name: Elizabeth Tipton
  affiliation: Department of Statistics, Northwestern University
- name: Matteo Parotto
  affiliation: Toronto General Hospital, UHN
date: "`r Sys.Date()`"
repository_url: https://github.com/awconway/zhf-review
twitter:
  creator: "@aw_conway"
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
# author:
#   - Aaron Conway PhD:
#       email: aaron.conway@utoronto.ca
#       institute: [PMCC, LBFON, QUT]
#       correspondence: true
#   - Megan Bittner BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Dan Phan BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Kristina Chang MScN:
#       institute: [TGH]
#       correspondence: false
#   - Elizabeth Tipton PhD:
#       institute: [NW]
#       correspondence: false
#   - Matteo Parotto MD:
#       institute: [TGH]
#       correspondence: false
# institute:
#   - PMCC: Peter Munk Cardiac Centre, University Health Network
#   - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   - QUT: School of Nursing, Queensland University of Technology (QUT)
#   - TGH: Toronto General Hospital, UHN
#   - NW: Department of Statistics, Northwestern University
# output:
#   bookdown::word_document2:
#     reference_docx: Extras/manuscript_template.docx
#     pandoc_args:
#       - --csl=Extras/anesthesiology.csl
#       - --lua-filter=Extras/scholarly-metadata.lua
#       - --lua-filter=Extras/author-info-blocks.lua
output: distill::distill_article
params:
  distill: TRUE
  word: FALSE
---

@@

Funding statement: Support was provided solely from institutional and/or departmental sources.

@@

```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path="figures/", include=params$distill, eval=params$distill}
# https://github.com/awconway/ggprisma
ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, full_text = 22, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
```

@@

Results from this systematic review have important implications for practice. Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature. It was reassuring that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QUADAS-2 tool were similar. As such, it is vital for clinicians considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation. If so, then it may not be appropriate to substitute the zero-heat-flux device in place of a core thermometer.

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
author:
- name: Aaron Conway
  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
  url: https://www.aaronconway.info
- name: Megan Bittner
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Dan Phan
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Navpreet Kamboj
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
- name: Kristina Chang
  affiliation: Toronto General Hospital, UHN
- name: Elizabeth Tipton
  affiliation: Department of Statistics, Northwestern University
- name: Matteo Parotto
  affiliation: Toronto General Hospital, UHN
date: "`r Sys.Date()`"
repository_url: https://github.com/awconway/zhf-review
twitter:
  creator: "@aw_conway"
output: distill::distill_article
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
# author:
#   - Aaron Conway PhD:
#       email: aaron.conway@utoronto.ca
#       institute: [PMCC, LBFON, QUT]
#       correspondence: true
#   - Megan Bittner BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Dan Phan BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Kristina Chang MScN:
#       institute: [PMCC]
#       correspondence: false
#   - Elizabeth Tipton PhD:
#       institute: [NW]
#       correspondence: false
#   - Matteo Parotto MD, PhD:
#       institute: [TGH, UoT]
#       correspondence: false
# institute:
#   - PMCC: Peter Munk Cardiac Centre, University Health Network
#   - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   - QUT: School of Nursing, Queensland University of Technology (QUT)
#   - NW: Department of Statistics, Northwestern University
#   - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN
#   - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto
# output:
#   bookdown::word_document2:
#     reference_docx: Extras/manuscript_template.docx
#     pandoc_args:
#       - --csl=Extras/anesthesiology.csl
#       - --lua-filter=Extras/scholarly-metadata.lua
#       - --lua-filter=Extras/author-info-blocks.lua
params:
  distill: TRUE
  word: FALSE
always_allow_html: true
---

@@

Funding statement: Support was provided solely from institutional and/or departmental sources. MP is supported by an Early Investigator Merit Award from the Department of Anesthesia, University of Toronto and Toronto General Hospital

@@

```{r fig-1,  fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path="figures/", include=params$distill, eval=params$distill}
# https://github.com/awconway/ggprisma
ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, full_text = 22, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
```

@@

This systematic review showed that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature. These results may have important implications for practice that clinicians should consider. It was reassuring that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QUADAS-2 tool were similar. As such, it is vital for healthcare professionals considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation. If so, then it may not be appropriate to substitute the zero-heat-flux device in place of a core thermometer.
